Architectures for workflow integration in science gateways

### 2016-04-11 paper.tex
Updates in section 3

@@

@@

See Figure~\ref{archi:tight}. The workflow engine is tightly
integrated with the science gateway, which means that it shares code,
framework components, libraries, etc. For instance, the workflow
engine might be a portlet in a Liferay portal, a controller in a Ruby
on Rails application, and so on. The workflow engine and the science
gateway usually share a database where application, users and other
resources are stored. In this model, task control and data control are
initiated from the science gateway. This is the model adopted in the
Catania Science Gateway Framework~\cite{Ardizzone2012} (see specific
documentation on
workflows\footnote{\url{http://bit.ly/1oQrzvQ}})
and LONI Pipeline Environment~\cite{dinov2009efficient}.\todo{Add better justification}

@@

=  Examples
* SHIWA CGI, but SHIWA CGI is more complex because it enables meta workflows. In general, if we wanted only to use an embedded workflow, we don't need the meta-workflow for that. 
* Maybe other tool integrations in CBRAIN or VIP. For instance FSL or any tool that can be parallelized by this is not exploited.

Refer to the recent paper from Kacsuk.

Command line tool can run anwywhere.
- Parallelization is tricky because command line tool can run anywhere, on any cluster. Sometimes, it is solved by wrapping workflow engine in another worfklow engine, to iterate, e.g. on subjects. That's what we do in VIP. But this is not ideal.
+ No extension required on the SG side to support a workflow engine, as long as it can wrap command line tools.

@@

@@

>>>>

Multi-engine, multi-language.

@@

%http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=4782949

@@

See Figure~\ref{archi:tight}. The workflow engine is tightly
integrated with the science gateway, which means that it is deployed
on the same machine and potentially shares code, libraries and other
software components with the science gateway. For instance, the
workflow engine might be a portlet in a Liferay portal, a controller
in a Ruby on Rails application, and so on. The workflow engine and the
science gateway usually share a database where application, users and
other resources are stored. In this model, task control and data
control are initiated from the science gateway. This is the model
adopted in the Catania Science Gateway Framework~\cite{Ardizzone2012}
(see specific documentation on
workflows\footnote{\url{http://bit.ly/1oQrzvQ}}),
CIPRES~\cite{miller2010creating} and LONI Pipeline
Environment~\cite{dinov2009efficient}.\todo{Add better justification}

@@

See Figure~\ref{archi:nested}. A nested workflow is an abstract
architectural pattern where an activity of a master workflow is itself
a workflow that is executed by another engine. Nested workflows can be
instantiated in the various architectures described previously. We
focus on instantiation with the service invocation model as this is
the most used architecture. The master workflow is also called
meta-workflow. The nested workflow might be described with a different
language than the one used to describe the master workflow.

Nested workflows have long been available in workflow engines, for
instance in the Taverna workbench~\cite{oinn2004taverna}. This model
was used by the SHIWA Simulation Platform to implement Coarse-Grained
workflow interoperability~\cite{terstyanszky2014enabling}, i.e. to
integrate various workflow engines in a consistent platform. Nested
workflows are also often used implicitly to wrap scripts as
black-boxes while these scripts actually correspond to complete workflows.

\begin{figure}
\centering
\def\svgwidth{0.48\columnwidth}
\input{images/nested-1.pdf_tex}
\def\svgwidth{0.48\columnwidth}
\input{images/nested-2.pdf_tex}
\caption{Nested workflows. Left: abstract model. Right: instantiation with service invocation.}
\label{archi:nested}
\end{figure}

@@

See Figure~\ref{archi:import}.

@@

\begin{figure}
\centering
\def\svgwidth{0.48\columnwidth}
\input{images/import-1.pdf_tex}
\def\svgwidth{0.48\columnwidth}
\input{images/import-2.pdf_tex}
\caption{Workflow import. Left: abstract model. Right: instantiation with service invocation.}
\label{archi:import}
\end{figure}
